A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
References update

Bio-inspired algorithms have been very successful when used to solve complex
optimization problems
\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
their complexity increases so does the computing power required
\cite{ontiveros2018high}. One strategy to address this processing need is to
use distributed computing \cite{thain2005distributed}, or the resources
available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
find the solution. This strategy gives us elasticity to adjust (increase or
reduce) the computing power to achieve a balance according to the nature of the
problem \cite{armbrust2010view}.

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
the previous task to finish before continuing. Some architectures address this
issue, what distinguishes us, is that our proposal presents an algorithm
designed in its entirety as a native solution in the cloud, fully distributed,
where its processes are executed in parallel and asynchronously. This technique
makes it easy to scale the computing power according to the complexity required
by the problem.

>>>>

Bio-inspired algorithms have been very successful when used to solve complex
optimization problems
\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
their complexity increases so does the computing power required
\cite{ontiveros2018high}. One strategy to address this processing need is to
use distributed computing \cite{thain2005distributed}, or the resources
available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
find the solution. This strategy gives us elasticity to adjust (increase or
reduce) the computing power to achieve a balance according to the nature of the
problem.

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
the previous task to finish before continuing. Some architectures address this
issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes us, is that our proposal presents an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.
